---
title: "Homework 6"
author: "Put your name here"
date: 'Due: see course timeline for due date'
output:
  html_document: default
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

# AI Policy Reminder and Note About New Approaches

Based on the syllabus policy, AI tools (e.g., ChatGPT) can be used on homework for code, but “if you do use such resources, then you must explicitly state where you got the code. For text, “you may not copy AI-generated text verbatim as responses on homework.” Any code or text that is discovered to be AI-generated and not explicitly cited will (a) be treated as a violation of the Elon Honor Code and (b) result in the lowest marking for the associated portion of the project rubric.

As a note, there are multiple ways to accomplish the tasks described in this assignment. If you use methods that we did not discuss in class (e.g., notes, activities, questions during class), you should explain where you learned your method and how it is accomplishing the task. For example, it's possible to subset data using "square bracket" notation. If I did this, I would say how I learned about it and why the code I used successfully subsets the data in the way I want.

---

Use the code chunk below to load any R libraries that you use in your script. I've added `dplyr` and `infer` as a start.

```{r, message = FALSE}
library(dplyr)
library(infer)
```

---

# Part 1 - NC Sports Betting

The Elon Poll [surveyed](https://eloncdn.blob.core.windows.net/eu3/sites/819/2023/06/Elon-Poll-Report-061423.pdf) registered voters in North Carolina on a variety of topics. One of those topics was whether sports betting should be legal in North Carolina. The code below creates a data frame with the results of their survey.

```{r}
betting <- data.frame(opinion = c(rep("support", 839),
                                  rep("oppose", 427)))
```

<br>

1. Calculate an estimate for the proportion of registered voters in North Carolina who support making sports betting legal.

```{r}

```

**Estimate:** 

<br>


2. Use the infer package to generate a bootstrap distribution of 1,000 sample proportions. Create a histogram of your distribution with your estimate from the previous question added to your graph. Don't forget to set a seed before your bootstrap distribution. 

```{r, out.width = "50%", fig.align = "center"}

```


<br> 

3. Describe important characteristics of your bootstrap distribution (e.g., shape, center, spread). Include why your estimate from the previous questions shows up where it does on your graph. 

**Description:** 


<br>

4. Calculate a 90% confidence interval based on your bootstrap distribution using either the percentile method or the standard error method. Report the interval below.

```{r}

```

**90% Confidence interval:** 

<br>


5. Explain how your chosen method creates confidence intervals as applied to this example. (Note: This does not mean to tell me what functions you used. Instead, you should briefly describe the process that creates the interval)

**Explanation:**

<br>


6. Write a sentence interpreting your confidence interval in context of this example.

**Interpretation:**

<br>


7. Suppose you shared your interval with state officials who decided the confidence interval was too wide for them to effectively reach conclusions. What are two things they could do to reduce the width of your confidence interval? For each option, what is a downside to using this option to reduce the CI width?

**Option 1 (include downside):** 

**Option 2 (include downside):** 


8. Calculate a **90%** confidence interval for this example using a theory-based method.

```{r}

```

**90% CI:** 

<br>


9. Is the theory-based interval you calculated similar to the bootstrap interval for the example above? Explain why or why not. (Hint: Consider how the intervals are constructed and which conditions have or have not been met.)

**Explanation:** 

<br>

---

# Part 2 - Climate Change Importance

The 2021 GSS asked respondents how important the issue of climate change was to them, ranging from 1 (not at all important) to 5 (extremely important). The mean value of the importance of climate change to respondents who had health insurance was 3.36 (s = 1.35, n = 6,609). The mean value for respondents who did not have health insurance was 3.17 (s = 1.36, n = 704). [Question from Statistics for Social Understanding, 2nd ed., by Whittier, Wildhagen, and Gold (2024)]

The following code simulates the data in R.

```{r}
set.seed(2021)
climate <- data.frame(climate_impt = c(rnorm(6609, mean=3.36, sd=1.35), 
                                       rnorm(704,  mean=3.17, sd=1.36)),
                      health_ins = c(rep("yes", 6609), rep("no", 704)))

# view the sample means
climate |> 
  summarize(mean = mean(climate_impt), .by = health_ins)
```

<br>


10. Suppose we want to compare the responses for those that have health insurance against those that do not. Use the `infer` package to create a bootstrap distribution for this situation, and then create a graph to visualize the distribution. Describe the distribution you create.

```{r}

```

**Graph description:** 

<br>


11. Generate 90% confidence intervals based on your bootstrap distribution. You should choose the option (percentile or standard error) that you **did not** use in Part 1. Report the interval below using proper notation.

```{r}

```

**90% CI:** 

<br>


12. Calculate a **90%** confidence interval for this example using a theory-based method. When reporting your interval, make sure to keep the order consistent with what you generated in the previous question.

```{r}

```

**90% CI:** 

<br>


13. Pick one of the intervals you created. Write a sentence interpreting your confidence interval in context of this example.

**Interpretation:** 

<br>


14. What is your overall takeaway based on your confidence interval? In other words, what can we say about the relationship between having health care insurance and the importance of climate change based on our sample?

**Answer:** 

<br> 


---

# Reflection


15. Answer one (or both) of the following questions. Be sure to give a complete answer to the question(s) you choose (i.e., more than just a sentence or two).

  - What's something from a recent set of notes that isn't entirely clear to you and what would it take to help solidify your understanding of the concept?
  - What's an example of how you've used confidence intervals in the past or envision using them in the future? What type of interval(s) did/will you use? What was/is the goal of using them in that context?
  
**Answer:**





